Multilevel regression models

### 2025-09-30 processing/03_prod_main_analysis.Rmd
to-ignore2

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
                    digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              # socialtrust="Social Trust",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              # "femaleFemale"="Female (Ref. = Male)",
              # "agenum"="Age",
              # "age2"="Age2",
             # "edyears"="Year of Education",
             # "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
             # "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")

@@

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table 1: Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups = 
         list("Social Class (Ref.= Service Class)" = 3:4,
              "Homogeneity × Social Class"=5:6),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/table001.html")
      )
```

@@

ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",

              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",

              "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
              "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",

              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality")

htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       caption = paste("Table 2: Multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: Individual level variables are centered within cluster (group mean).Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 2:3,
                    "Homogeneity × Social Class"=5:6, 
                    "Class × Income Inequality" = 8:9 ,
                    "Homogeneity × Social Class × Income Inequality"=10:11),
      custom.gof.rows = list("Controls"=rep("Yes",2)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual"),
        file = here::here("output/tables/table002.html"))
```

@@

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  Q03pcm,
  edyears,
  female,
  agenum,
  partner,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") 
dfreg <- na.omit(dfreg)
dfreg$egal <- as.numeric(scale(dfreg$egal))
## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+partner+edyears+Q03pcm+workst+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,digclas1_VW_3,
digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              # socialtrust="Social Trust",
              "femaleFemale"="Female (Ref. = Male)",
              "agenum"="Age",
              # "age2"="Age2",
             "edyears"="Year of Education",
             "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
             "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
             "partnerHas a partner" = "Has partner (Ref.= No partner)",
                           "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              # "unionYes" ="Union Membership (Ref. = Not Unionized)",
              # "dclass3spo_VIntermediate class (III+IV)" = "Intermediate Class (Partner)",
              # "dclass3spo_VWorking Class (V+VI+VII)" = "Working Class (Partner)",              
              # "dclass3spo_VNo information (Missing, No partner)" = "No information (Not available, No partner)",
              "homclass3_V_res:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_res:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class")

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table A1: Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
      groups = list("Household Income (Ref.= Tertile I)"= 6:8,
                    "Social Class (Ref.= Service Class)" = 11:12, 
                    # "Partner's Social Class (Ref.= Service Class)" = 12:14,
                    "Homogeneity x Social Class"=13:14),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableA1.html")
      )
```

>>>>

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + dclass3res_V + female+agenum+know_total+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass3res_V)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

digclas1_VW_7 <- update(digclas1_VW_0, . ~ . +dclass3res_V*homclass3_V_res+know_total)
digclas1_VW <- list(digclas1_VW_0,
                    # digclas1_VW_1,
                    # digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list("(Intercept)"= "(Intercept)",
  "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              homclass3_V_res="Class-based network homogeneity",
              "dclass3res_VIntermediate class (III+IV):homclass3_V_res" = "Intermediate Class × Homogeneity",
              "dclass3res_VWorking Class (V+VI+VII):homclass3_V_res" = "Working Class × Homogeneity"
)

@@

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table 1: Multilevel models for social class, network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups =
         list("Social Class (Ref.= Service Class)" = 2:3,
              "Social Class × Homogeneity"=5:6),
      custom.gof.rows = list("Controls"=c(rep("Yes",2))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/table001.html")
      )
```

@@

ccoef <- list("dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              homclass3_V_gc="Class-based network homogeneity",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",
              "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
              "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality")

htmlreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       caption = paste("Table 2: Multilevel models for income inequality, social class, network homogeneity and redistributive preferences"),
       custom.note = " Note: Individual level variables are centered within cluster (group mean).Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 1:2,
                    "Social Class × Homogeneity"=4:5,
                    "Class × Income Inequality" = 8:9 ,
                    "Social Class × Homogeneity × Income Inequality"=10:11),
      custom.gof.rows = list("Controls"=rep("Yes",2)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual"),
        file = here::here("output/tables/table002.html"))
```

@@

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
   prefineq,redist,
  egal = egal2,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  female,
  agenum,
  Q03pcm,
  edyears,
  partner,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)
         ) %>%
  filter(country2 != "SVN") 
dfreg$egal <- as.numeric(scale(dfreg$egal))
dfreg_1 <- na.omit(dfreg %>% dplyr::select(prefineq,redist,
  egal,
  dclass3res_V,
  homclass3_V_res,
  know_total,
  female,
  agenum,
  WEIGHT,
  region,country2)
  )

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + (1|country2),data=dfreg_1,weights = WEIGHT)
digclas1_VW_2 <- update(digclas1_VW_0, . ~ . + dclass3res_V)
digclas1_VW_3 <- update(digclas1_VW_2, . ~ . + dclass3res_V+homclass3_V_res+female+agenum+know_total)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass3res_V*homclass3_V_res)
#Include additional controls
digclas1_VW_8 <- update(digclas1_VW_7, . ~ . + edyears+Q03pcm+partner+workst,data=na.omit(dfreg))
digclas1_VW <- list(digclas1_VW_2,digclas1_VW_3,digclas1_VW_7,digclas1_VW_8)

ccoef <- list("dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
             "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              "dclass3res_VIntermediate class (III+IV):homclass3_V_res" = "Intermediate Class × Homogeneity",
              "dclass3res_VWorking Class (V+VI+VII):homclass3_V_res" = "Working Class × Homogeneity",
             "edyears"="Year of Education",
             "Q03pcmT02"="Income (T2)","Q03pcmT03"="Income (T3)","Q03pcmMissing"="Income (No information)",
             "workstNot in paid work" = "Not in paid work (Ref. = In paid work)",
             "partnerHas a partner" = "Has partner (Ref.= No partner)",
             "femaleFemale"="Female (Ref. = Male)",
             "agenum"="Age"
             )

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table A1: Multilevel models for network homogeneity and redistributive preferences"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 1:2,
                    "Social Class × Homogeneity"=5:6,
                    "Household Income (Ref.= Tertile I)"= 8:10
                    ),
      custom.gof.rows = list("Controls"=c(rep("Yes",4))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableA1.html")
      )
```
